R Notebook

### 2021-09-14 documentation_and_analysis/draftbook.Rmd
Plot - EV vs Time in UK plot complete

```{r}
uk_ev_map %>% 
  leaflet() %>% 
  setView(lng = -4.2026, lat = 55.8, zoom = 4.7, options = list()) %>%
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addPolygons(fillColor = ~pal(x2021_q1),
    weight = 0.1,
    opacity = 0.9, 
    color = "black",
    fillOpacity = 0.8,
    highlightOptions = highlightOptions(color = "green", weight = 2,
                                        bringToFront = TRUE),
    label = uk_ev_map_labels,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>% 
  addLegend(pal = pal, values = ~x2021_q1, opacity = 0.7, title = NULL,
            position = "bottomright")
```

>>>>

```{r}
# Geospatial of EV Vehicles in the UK 2021 Q1
uk_ev_map %>% 
  leaflet() %>% 
  setView(lng = -4.2026, lat = 55.8, zoom = 4.7, options = list()) %>%
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addPolygons(fillColor = ~pal(x2021_q1),
    weight = 0.1,
    opacity = 0.9, 
    color = "black",
    fillOpacity = 0.8,
    highlightOptions = highlightOptions(color = "green", weight = 2,
                                        bringToFront = TRUE),
    label = uk_ev_map_labels,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>% 
  addLegend(pal = pal, values = ~x2021_q1, opacity = 0.7, title = NULL,
            position = "bottomright")
```

```{r}
# Wrangling to create an EV count over time plot 
uk_ev_longer <- uk_ev %>%
  # Pivot longer to get year and count columns
  pivot_longer(cols = c(x2021_q1:x2011_q4), names_to = c("year"), values_to = "no_of_ev") %>% 
  # Filter so we only have UK as a whole data AND we only want final numbers of the year so Q4 
  filter(region_local_authority_apr_2019_3 == "United Kingdom" & str_detect(year, "q4")) %>% 
  # Simplify to just show year
  mutate(year = case_when(str_detect(year, "2021") ~ "2021",
         str_detect(year, "2020") ~ "2020",
         str_detect(year, "2019") ~ "2019",
         str_detect(year, "2018") ~ "2018",
         str_detect(year, "2017") ~ "2017",
         str_detect(year, "2016") ~ "2016",
         str_detect(year, "2015") ~ "2015",
         str_detect(year, "2014") ~ "2014",
         str_detect(year, "2013") ~ "2013",
         str_detect(year, "2012") ~ "2012",
         str_detect(year, "2011") ~ "2011"),
         year = as.numeric(year),
         no_of_ev = as.numeric(no_of_ev))
```

```{r}
uk_ev_longer %>% 
  ggplot() +
  aes(x = year, y = no_of_ev) +
  geom_col(fill = "lawngreen") +
  scale_x_continuous(breaks = c(2011:2020)) +
  scale_y_continuous(breaks = seq(0, 220000, by = 20000), limits = c(0, 220000)) +
  labs(title = "\nNumber of Electric Vehicles over time in the UK\n",
       x = "\nYear\n",
       y = "\nNumber of Electric Vehicles\n") +
  theme_minimal() 
```
